\name{}: machine learning over interaction networks and ontology-based background knowledge predicts drug--target interactions

### 2021-04-27 paper/main.tex
Update t-test for DTI-CDF

\title[\name{}]{\name{}: machine learning over interaction networks and
  ontology-based background knowledge predicts drug--target
  interactions}
\author[Hinnerichs \& Hoehndorf]{Tilman Hinnerichs\,$^{\text{\sfb 1,}*}$ and Robert
  Hoehndorf\,$^{\text{\sfb 2}}$}
\address{$^{\text{\sf 1}}$Department, Institution, City, Post Code, Country and \\
  $^{\text{\sf 2}}$Computational Bioscience Research Center, Computer,
  Electrical and Mathematical Sciences \& Engineering Division, King
  Abdullah University of Science and Technology, 4700 King Abdullah
  University of Science and Technology, Thuwal 23955, Saudi Arabia.}

@@

Considering Macro AUCs, \name{} improves significantly ($p<10^{-4}$,
one-sided t-test) over MolTrans ($t=36.6$), DeepDTI ($t=40.5$),
DeepDTA ($t=36.6$), and DeepConv-DTI ($t=40.5$) on the BioSnap
dataset, and significantly ($p<10^{-4}$, one-sided t-test) over DTINet
($t=20.8$) and DTIGEMS+ ($t=18.0$) on the Yamanishi dataset; DTI-CDF
performs better than \name{} ($p=0.02$, one-sided t-test).  We further
perform another one-tailed t-test to compare $MicroAUC_p$
performance. We find that \name{} improved significantly
($p < 10^{-4}$) over MolTrans($t=21.2$), DeepDTI ($t=31.0$), DeepDTA
($t=33.4$), and DeepConv-DTI ($t=23.7$) on the BioSnap dataset, and
over DTINet ($t=29.6$), DTIGEMS+ ($t=28.0$), and DTI-CDF ($t=9.5$) on
the Yamanishi dataset.

>>>>

\title[\name{}]{\name{}: machine learning over interaction networks and
  ontology-based background knowledge predicts drug--target
  interactions}
\author[Hinnerichs \& Hoehndorf]{Tilman Hinnerichs\,$^{\text{\sfb 1,}*}$ and Robert
  Hoehndorf\,$^{\text{\sfb 1}}$}
\address{$^{\text{\sf 1}}$Computational Bioscience Research Center, Computer,
  Electrical and Mathematical Sciences \& Engineering Division, King
  Abdullah University of Science and Technology, 4700 King Abdullah
  University of Science and Technology, Thuwal 23955, Saudi Arabia.}

@@

Considering Macro AUCs, \name{} improves significantly ($p<10^{-4}$,
one-sided t-test) over MolTrans ($t=36.6$), DeepDTI ($t=40.5$),
DeepDTA ($t=36.6$), and DeepConv-DTI ($t=40.5$) on the BioSnap
dataset, and significantly ($p<10^{-4}$, one-sided t-test) over DTINet
($t=20.8$) and DTIGEMS+ ($t=18.0$) on the Yamanishi dataset; DTI-CDF
performs better than \name{} ($p=0.1, t=1.3$, one-sided t-test) \todo{significance}.  We further
perform another one-tailed t-test to compare $MicroAUC_p$
performance. We find that \name{} improved significantly
($p < 10^{-4}$) over MolTrans($t=21.2$), DeepDTI ($t=31.0$), DeepDTA
($t=33.4$), and DeepConv-DTI ($t=23.7$) on the BioSnap dataset, and
over DTINet ($t=29.6$), DTIGEMS+ ($t=28.0$), and DTI-CDF ($t=9.5$) on
the Yamanishi dataset.
